SVG: The Paper

### 2022-04-20 Analysis/index.Rmd
removing Tagoooo

## Clarke et al (2022)

@@

### Calibration

@@

### Examples of Trials

@@

## QJEP Dataset

```{r echo = TRUE}
# Reimport data again (as we removed the inital target selection earlier)
d <- read_csv("data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
  filter(found == 1) %>%
  mutate(condition = as_factor(condition))
```

@@

We can model this as a mixture of Gaussians.

## Tagu dataset

```{r}
d <- read_csv("data/tagu_2020_prox_mouse.csv", show_col_types = FALSE) %>%
  filter(found == 1) %>%
  mutate(condition = as_factor(condition))

plt_all + plt_med 
```

## Item Density

>>>>

@@

## Calibration

@@

## Examples of Trials

@@

Previous work (cite Clarke and Tatler etc) has demonstrated that the initial fixation in scene viewing can be well described with truncated Gaussian distribution. Here we explore using a similar idea to account for starting locations.

```{r echo = TRUE}
# Reimport data again (as we removed the initial target selection earlier)
d <- read_csv("data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
  filter(found == 1) %>%
  mutate(condition = as_factor(condition))
```

@@

We can model this as multi-level Gaussian? Yes, although it seems like people are in one of two clusters.

```{r fig.cap = "The mean posterior plot for the truncated normal distriubtions for (*left*) $x$ and (*right*) $y$. We can see that a two component mixture model will capture most of the variance in intial target selection."}

m <- readRDS("scratch/init_sel_model.rds")
z <- seq(0, 1, 0.01)

gather_draws(m, u[dim, observer]) %>% 
  ungroup() %>%
  select(-.variable) %>%
  rename(obs_b = ".value") %>%
  full_join(gather_draws(m, b[dim]),
             by = c("dim", ".chain", ".iteration", ".draw")) %>%
  mutate(obs_b = .value + obs_b,
         .variable = if_else(dim %in% c(1,2), "mu", "sd"),
         dim = if_else(dim %in% c(1,3), "x", "y")) %>%
  select(observer, dim, .iteration, obs_b, param = ".variable") %>%
  mutate(obs_b = if_else(param == "sd", exp(obs_b), obs_b)) -> a

a %>% group_by(observer, param, dim) %>%
  summarise(value = mean(obs_b) , .groups = "drop") %>%
  pivot_wider(names_from = param, values_from = value) %>%
  rename(mean = "mu") -> am

create_post_plot <- function(dm) {

  pmap(filter(am,  dim == dm) %>% select(mean, sd), dtruncnorm, a = 0, b= 1, x = z) %>%
    set_names(rownames(filter(am,  dim == dm))) %>%
    bind_rows() %>%
    mutate(z = z) %>%
    pivot_longer(-z, names_to = "observer", values_to = "v") %>%
    ggplot(aes(x = z, y = v, group = observer)) + geom_path(alpha = 0.25) +
    scale_x_continuous(dm) + scale_y_continuous("likelihood") -> plt

  return(plt)
}

create_post_plot("x") + create_post_plot("y")
```

Do we want to simplify this model to something in which people have some mix of a (fixed) centre and corner bias?

# Item Density
